The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multiphase Forest Inventories

### 2017-09-04 JStatSoft_forestinventory_master-concordance.tex

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 104 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 112:%
1 94 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 207:%
120 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 217:%
1 75 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 293:%
131 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 305:%
1 126 1 1 2 4 0 1 2 14 1 1 5 7 0 1 2 2 1 1 2 24 0 1 2 4 1 1 2 4 0 1 2 2 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 157 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 5 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 836:%
144}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 837:%
1 119 1 1 2 8 0 1 2 4 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 4 1 1 4 6 0 1 2 2 1 1 2 8 0 1 2 193 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 11 0 1 3 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 7 1 1 7 10 0 1 3 2 1 1 2 12 0 1 2 6 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1356:%
146 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1368:%
1 42 1 1 2 11 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1433:%
159 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1443:%
1 20 1 1 2 4 0 1 2 4 1 1 6 8 0 1 2 4 1 1 6 8 0 1 2 18 1 1 8 16 1 1 7 9 0 1 2 2 1 1 2 8 0 1 2 2 1 1 2 8 0 1 2 4 1 1 2 8 0 1 2 22 1 1 3 5 0 1 2 27 1 1 3 5 0 1 2 39 1 1 3 5 0 1 2 23 1 1 3 5 0 1 2 19 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1740:%
170 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1750:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 36 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 2008:%
181 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 2017:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 2022:%
191 11 1}

>>>>

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 104 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 112:%
1 94 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 207:%
120 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 217:%
1 75 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 293:%
131 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 305:%
1 126 1 1 2 4 0 1 2 14 1 1 5 7 0 1 2 2 1 1 2 24 0 1 2 4 1 1 2 4 0 1 2 2 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 157 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 5 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 836:%
144}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 837:%
1 119 1 1 2 8 0 1 2 4 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 4 1 1 4 6 0 1 2 2 1 1 2 8 0 1 2 193 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 11 0 1 3 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 7 1 1 7 10 0 1 3 2 1 1 2 12 0 1 2 6 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1356:%
146 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1368:%
1 42 1 1 2 11 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1433:%
159 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1443:%
1 20 1 1 2 4 0 1 2 4 1 1 6 8 0 1 2 4 1 1 6 8 0 1 2 18 1 1 8 16 1 1 7 9 0 1 2 2 1 1 2 8 0 1 2 2 1 1 2 8 0 1 2 4 1 1 2 8 0 1 2 22 1 1 3 5 0 1 2 27 1 1 3 5 0 1 2 39 1 1 3 5 0 1 2 23 1 1 3 5 0 1 2 19 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1740:%
170 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1750:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1981:%
181 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 1990:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1995:%
191 11 1}

### 2017-09-04 rnw/Calculation of Confidence Intervals.Rnw

Converting the estimated variance into a 95\% \textit{confidence interval} (CI) allows for an intuitive and practice-oriented interpretation of the uncertainties associated to a point estimate. The correct interpretation of a CI is not that there is a 95\% probability that it contains the true value.  In the design-based context, the true value of the population parameter we are trying to estimate, albeit unknown, is fixed and the sample is randomly generated under the sampling design. Theoretically, if we were to repreatedly conduct the inventory using the same estimation method, estimator and auxiliary information under newly drawn random samples, and then calculate 95\%  CIs from each sample, then 95\% of them are expected to contain the true population parameter. The confidence level $1-\alpha$ (e.g. 95\%) is thus the frequency or proportion of possible confidence intervals that contain the unknown population parameter and is therefore often also referred to as \textit{coverage rate}. For a user, the CI is a measure of precision that can also be used for hypothesis testing, i.e. providing evidence that an estimate is statistically different from a given value if that value lies outside the CI boundaries.

@@

where $\hat{Y}$ is the point estimate, $\var(\hat{Y})$ is the estimated variance, and $1-\alpha$ is the confidence level. Note that for three-phase sampling, $p$ constitutes the number of parameters used in the \textit{full} regression model. In case of cluster-sampling, $n_{2,G}$ is the number of terrestrial clusters (a cluster constitutes the sample unit and comprises multiple sample plots). In the package, the confidence intervals for all estimation methods and estimators can be computed by the S3 generic function \code{confint()}, which requires an estimation object created by the \code{onephase()}, \code{twophase()} or \code{threephase()} function. For example, the 95\% confidence interval for the small area estimates by the \textit{extpsynth} estimator (section \ref{sec:twophase_sae}) be applied by:

>>>>

Converting the estimated variance into a 95\% \textit{confidence interval} (CI) allows for an intuitive and practice-oriented interpretation of the uncertainties associated to a point estimate. The correct interpretation of a CI is not that there is a 95\% probability that it contains the true value.  In the design-based context, the true value of the population parameter we are trying to estimate, albeit unknown, is fixed and the sample is randomly generated under the sample design. Theoretically, if we were to repreatedly conduct the inventory using the same estimation method, estimator and auxiliary information under newly drawn random samples, and then calculate 95\%  CIs from each sample, then 95\% of them are expected to contain the true population parameter. The confidence level $1-\alpha$ (e.g. 95\%) is thus the frequency or proportion of possible confidence intervals that contain the unknown population parameter and is therefore often also referred to as \textit{coverage rate}. For a user, the CI is a measure of precision that can also be used for hypothesis testing, i.e. providing evidence that an estimate is statistically different from a given value if that value lies outside the CI boundaries.

@@

where $\hat{Y}$ is the point estimate, $\var(\hat{Y})$ is the estimated variance, and $1-\alpha$ is the confidence level. Note that for three-phase sampling, $p$ constitutes the number of parameters used in the \textit{full} regression model. In case of cluster-sampling, $n_{2,G}$ is the number of terrestrial clusters (a cluster constitutes the sample unit and comprises multiple sample plots). In the package \pkg{forestinventory}, the confidence intervals for all estimation methods and estimators can be computed by the S3 generic function \code{confint()}, which requires an estimation object created by the \code{onephase()}, \code{twophase()} or \code{threephase()} function. For example, the 95\% confidence interval for the small area estimates by the \textit{extpsynth} estimator (section \ref{sec:twophase_sae}) are calculated by:

### 2017-09-04 rnw/Twophase_Estimators and their Application.Rnw

An extension to the so-far published estimators by Mandallaz is the consideration of a \textit{\textbf{boundary adjustment}} according to forest/non-forest decision on the support level, which can be optionally applied in the \code{twophase()} and \code{theephase()} function of the package. In forest inventories, the sample is often restricted to those sample locations located within the forest area. In case a consistent forest definition can be applied to both the $s_2$ and $s_1$ sample (e.g. by a ploygon forest mask layer), it might be desired to restrict the calculation of the explanatory variables to the forest area within the given support (figure \ref{fig:exh_nexh_bw}). This method was suggested in \citet{mandallaz2013b} and led to an improvement of the regression model accuracy. To  insure  an  unbiased  calculation  of  the mean of $\pmb{Z}$, the  respective mean have then to be calculated as the \textit{weighted} mean according to equation \ref{eq:wmeanZ}. The weight $w(x)$ is thereby equal to the percentage of forested area within the support of sample location $x$.

>>>>

An extension to the so-far published estimators by Mandallaz is the consideration of a \textit{\textbf{boundary adjustment}} according to forest/non-forest decision on the support level, which can be optionally applied in the \code{twophase()} and \code{threephase()} function of the package. In forest inventories, the sample is often restricted to those sample locations located within the forest area. In case a consistent forest definition can be applied to both the $s_2$ and $s_1$ sample (e.g. by a ploygon forest mask layer), it might be desired to restrict the calculation of the explanatory variables to the forest area within the given support (figure \ref{fig:exh_nexh_bw}). This method was suggested in \citet{mandallaz2013b} and led to an improvement of the regression model accuracy. To  insure  an  unbiased  calculation  of  the mean of $\pmb{Z}$, the  respective mean have then to be calculated as the \textit{weighted} mean according to equation \ref{eq:wmeanZ}. The weight $w(x)$ is thereby equal to the percentage of forested area within the support of sample location $x$.
